|

### 2021-06-29 supplementary_information_pnas.Rmd
Update supplementary_information_pnas.Rmd

We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed). We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$. In this simulation, presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$. Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016]. We calculated % bias of estimated asymptotic species richness $S_{est}$:

>>>>

We evaluated sensitivity of asymptotic species richness (Chao 2 estimator) to sample size (i.e., the number of sampling sites in a watershed). We simulated presence-absence data of species with known values of true species richness $S_{true}$ and the number of sampling sites $N_{site}$. In this simulation, the presence of species $i$ at site $x$, $J_{ix}$, was drawn from a Bernoulli distribution as $J_{ix} \sim Bernoulli(p_{i}\kappa_{ix})$ where $p_i$ is the detection probability for species $i$ and $\kappa_{ix}$ is the presence probability of species $i$ at site $x$. Based on the incidence frequency of simulated species $F_i = \sum_{x = 1}^{N_{site}}J_{ix}$, we estimated asymptotic species richness using the iNEXT function in the R package 'iNEXT' [@hsiehINEXTPackageRarefaction2016]. We calculated % bias of estimated asymptotic species richness $S_{est}$:
